\textls[-15]{\thetitle \mbox{(Technical Report)}}

### 2022-11-10 lang-design.tex
Reply the comment.

Note that the proof term generated by \lsti{fdiscriminate H} in "STLC"
is reusable by family "STLCFix", because the partial recursor and its
equalities are compatible with the late binding of "tm".
Also note that within family "STLCFix", a second partial recursor
(called "tm_prect_STLCFix") and its equalities are available,
allowing properties about "tm_fix",
such as \lsti{\neg(tm_var "x" = tm_fix "y" t)}, to be proved.\EDJ{Actually this one is provable using the first partial recursor because LHS is "Some sth" RHS is "None". An approrpiate example is STLC_bool where "tm_true = tm_false" because using first partial recursor both will reduced to "None", only the second partial recursor can distinguish them.}\YZreply{To avoid introducing another family, can we use \lsti{tm_fix x t = tm_fix x' t' -> t = t'} as an example?}

>>>>

Note that the proof term generated by \lsti{fdiscriminate H} in "STLC"
is reusable by family "STLCFix", because the partial recursor and its
equalities are compatible with the late binding of "tm".
Also note that within family "STLCFix", a second partial recursor
(called "tm_prect_STLCFix") and its equalities are available,
allowing properties about "tm_fix",
such as \lsti{\neg(tm_var "x" = tm_fix "y" t)}, to be proved.\EDJ{Actually this one is provable using the first partial recursor because LHS is "Some sth" RHS is "None". An approrpiate example is STLC_bool where "tm_true = tm_false" because using first partial recursor both will reduced to "None", only the second partial recursor can distinguish them.}\YZreply{To avoid introducing another family, can we use \lsti{tm_fix x t = tm_fix x' t' -> t = t'} as an example?}\EDJreply{That is fine I think. I think you already declared the existence of ``finjection'' earlier.}
